Environmental behaviour & practices

### 2021-01-19 01-Sustainable-indicators.Rmd
references and adding elements de plavlo

<!-- Problem -->
However, the evaluation of pertinent sustainable indicators for this short supply networks is one the  major topic of discussion in the scientific and practitioners communities. 
The problem relies in the selection of these 'pertinent' sustainable indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
Moreover, depending of the material or product and their technological process associated to, this entakes difficulties in terms of dependance of stakeholders beyond the scope of the short circuit.

<!-- Contex -->
The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@Santander2020]. 
The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to foster the use of certains plastic waste materials in order to extend eventually (multiple) lifecycle for a printed product. 
More precisely, the use of recycled assets in the printing process chain of additive manufacturing technology can give add value to wastes to create possible final products or even scientific equipement [@Pearce2020a] a a lower cost than the commercial.
In a sense, this approach could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe, even if this intervention remains largely case-dependent.

<!-- Conceptual Framework -->
Nevertheless, there remain a gap in the scientific literature to define in what sense DRAM could be considered as sustainable transition in the global aspect of the term. 
The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
enhancing human well-being to more equitably meet the needs of both current and future generations.
@Clark2020 developed an integrative framework for sustainability considering five major pilards: 
(1) environment and development, 
(2) governance, 
(3) complexity, and 
(4) context dependence.
At the core of research on sustainability are the intertwined nature–society interactions.
Sustainability science research has focused on the four key elements involved in those interactions:

@@

Therefore, contextualizing thi sustainable concptual framework to the DRAM context, the main research question is for this project are:

@@

>>>>

<!-- Problem -->
However, the evaluation of pertinent sustainable indicators for this short supply networks is one the  major topic of discussion in the scientific and practitioners communities. 
The problem relies in the selection of 'pertinent' sustainable indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
Moreover, depending of the material or product and their technological process associated to, this entakes difficulties in terms of dependance of stakeholders beyond the scope of the short circuit.

<!-- Contex -->
The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@Santander2020]. 
The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to foster the use of certains plastic waste materials in order to extend eventually (multiple) lifecycle for a printed product. 
More precisely, the use of recycled assets in the printing process chain of additive manufacturing technology can give add value to wastes to create possible final products or even scientific equipement [@Pearce2020a] at a lower cost than the commercial.
In a sense, this approach could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe, even if this intervention remains largely case-dependent.

<!-- Conceptual Framework -->
Nevertheless, there remain a gap in the scientific literature related to in what extend the DRAM could be considered as sustainable in the global aspect of the term. 
The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
enhancing human well-being to more equitably meet the needs of both current and future generations.
@Clark2020 developed an integrative framework for sustainability considering five major pilards: 
(1) environment and development, 
(2) governance, 
(3) complexity, and 
(4) context dependence.
At the core of research on sustainability, there are a intertwined nature–society interactions.
Sustainability science research has focused on the four key elements involved in the interactions of:

@@

Therefore, contextualizing the sustainable conceptual framework to the DRAM context, the main research questions for this project are:

@@

## LCA

- Review on LCA [@Visentin2020]

### 2021-01-19 02-supply-chain.Rmd
sustainable indicator PPS&Q V1.0.0
adding the minmapping for all
references and adding elements de plavlo

---
title: "Supply chain Axis"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 02-supply-chain.bib
#nocite: '@*'

@@

## Rational

>>>>

---
title: "Supply chain Axis"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 02-supply-chain.bib
bibliography: library.bib
#nocite: '@*'

@@

:::l-page
<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
:::

# Rationale

A new paradigm of plastic recycling, called distributed plastic recycling, has emerged in the literature in order to face the socio-environmental challenges related to plastic waste management. Under this new model of small recycling centers, the main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. To do so, the use of additive manufacturing enables the technical paths.

  However, as with any recycling system, its feasibility must be evaluated before its implementation. Although research has been conducted regarding the technical feasibility of distributed plastic recycling, little is known about its feasibility from the supply chain perspective [@CruzSanchez2020] and its impact in ecosystem services. 
From a supply chain perspective, the feasibility evaluation for the establishment of recycling networks should be oriented towards sustainable development. 
In addition, the notion of sustainability could be used as a framework to analyze and manage the impact of human activities (or supply chain) on ecosystem services [@Abson2014].
A network is sustainable, if it integrates the economic, environmental and social dimensions, traditionally referred to as the three pillars of sustainability (’triple bottom-lines - TBL) (Hacking and Guthrie, 2008). 
In addition, @Bautista2016 proposes the integration of political and technological dimensions (TBL+) if they have a great importance in the system to evaluate.. However, literature reviews about supply chains networks highlight : 
(1) the little consideration of social, technological and political aspects in sustainability assessments, and 
(2) the great consideration of economic and environmental aspects 
[@EspinozaPerez2017c, @Fonseca2018, @Moreno-Camacho2019].

This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

The purpose of this research is to explore and assess the local impact, considering sustainability dimensions and ecosystem services, derived from the implementation of a distributed plastic recycling chain. 
The study intends to research, based on the notion of sustainability, which and how the ecosystem services are impacted due to the implementation of the plastic recycling chain proposed. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches

This study seeks to address the following questions:

- What are the appropriate ecosystem service indicators for assessing distributed plastic recycling? 
- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?

## Ideas

### 2021-01-19 03-comportements.Rmd
references and adding elements de plavlo

---
title: "Environmental behaviour & practices"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 03-comportement.bib
#nocite: '@*'

>>>>

---
title: "Environmental behaviour & practices"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 03-comportement.bib
bibliography: library.bib
#nocite: '@*'
